Data Specialization for a Staged Lambda Calculus

### 2015-02-23 paper/intro.tex

\emph{Data specialization} \cite{knoblock96,jorring86} 
is a technique for specializing $f$ \emph{without} the fixed argument $a$,
instead splitting $f$ into a pair of functions $f_1$ and $f_2$. $f_1(a)$
produces a data structure containing the results of the computations which
depend only on $a$; $f_2$ then completes the computation, given this data
structure and the varying argument; that is, $f_2(f_1(a),-)$ computes $f(a,-)$.

>>>>

\emph{Data specialization} \cite{knoblock96,JS86-staging} 
is a technique for specializing $f$ \emph{without} the fixed argument $a$,
instead splitting $f$ into a pair of functions $f_1$ and $f_2$. $f_1(a)$
produces a data structure containing the results of the computations which
depend only on $a$; $f_2$ then completes the computation, given this data
structure and the varying argument; that is, $f_2(f_1(a),-)$ computes $f(a,-)$.
Crucially, none of the generated code ($f_1$ or $f_2$) depends on $a$!
